Test Document

### 2024-11-27 test.Rmd
new test for colouring links

```{r simulation_1, echo=FALSE, warning=FALSE, message=FALSE}
#SLOW COMPUTATION.. FOR FAST COMPUTE SEE LINES 11, 20, 65, & 79 
# Load required libraries
if (!require("reshape2")) install.packages("reshape2")
if (!require("ggplot2")) install.packages("ggplot2")
library(reshape2)
library(ggplot2)
# Define reaction rates
c1 <- (37 / 1e6) * 10             # Formation of CPD
c2 <- (2 / 1e6) * 10              # Formation of 64-PP
c3 <- (1 - (37 + 2) / 1e6) * 10   # No dimerization occurs// REMOVE THIS LINE FOR FAST COMPUTE

# Initial state
state <- c(T1 = 10000, T2 = 10000, CPD = 0, `64PP` = 0)
# Define propensity functions
propensities <- function(state) {
  c(
    c1 * state["T1"] * state["T2"], # Reaction 1
    c2 * state["T1"] * state["T2"],  # Reaction 2
    c3 * state["T1"] * state["T2"]  #Reaction 3   // REMOVE THIS LINE FOR FAST COMPUTE
  )
}
# Gillespie simulation function
simulate_gillespie <- function(state, max_time) {
  # Initialize time and output data frame
  time <- 0
  output <- data.frame(
    Time = numeric(0),
    T1 = numeric(0),
    T2 = numeric(0),
    CPD = numeric(0),
    `64PP` = numeric(0)
  )

  # Record the initial state
  initial_row <- c(Time = time, state)
  output <- rbind(output, as.data.frame(t(initial_row), stringsAsFactors = FALSE))

  while (time < max_time) {
    # Calculate propensities
    props <- propensities(state)
    total_prop <- sum(props)

    # Stop if no reactions can occur
    if (total_prop == 0) break

    # Time to next reaction
    delta_t <- rexp(1, rate = total_prop)
    time <- time + delta_t

    # Select which reaction occurs
    reaction <- sample(length(props), 1, prob = props)

    # Update state based on reaction
    if (reaction == 1) {
      state["T1"] <- state["T1"] - 1
      state["T2"] <- state["T2"] - 1
      state["CPD"] <- state["CPD"] + 1
    }
    if (reaction == 2) {
      state["T1"] <- state["T1"] - 1
      state["T2"] <- state["T2"] - 1
      state["64PP"] <- state["64PP"] + 1
    }
    if (reaction == 3) {   #REMOVE THIS SECTION FOR QUICK COMPUTE
      next
    }

    # Record the new state
    new_row <- c(Time = time, state)
    output <- rbind(output, as.data.frame(t(new_row), stringsAsFactors = FALSE))
  }

  # Convert columns to numeric for consistency
  output[] <- lapply(output, as.numeric)
  return(output)
}
# Run the simulation
max_time <- 10        #SET TO HIGHER TIME IF DOING FAST COMPUTE
simulation <- simulate_gillespie(state, max_time)
```

```{r graph_1, echo=FALSE, warning=FALSE, message=FALSE}
# Reshape data for plotting
simulation_long <- melt(simulation, id.vars = "Time")
# Plot results
ggplot(simulation_long, aes(x = Time, y = value, color = variable)) +
  geom_line() +
  labs(
    title = "Dimerization Reaction Set Simulation",
    x = "Time",
    y = "Molecule Count",
    color = "Species"
  ) +
  theme_minimal()
```
```{r}
# Display the first few rows of the simulation data
knitr::kable(head(simulation), format = "html", caption = "Simulation Results (First Few Rows)")
```

>>>>

---
title: "Test Document"
output:
  pdf_document:
    keep_tex: true
header-includes:
  - \usepackage{xcolor}
  - \usepackage{hyperref}
  - \hypersetup{colorlinks=true, linkcolor=red, citecolor=green, urlcolor=blue}
---

This is a test document. See Figure \ref{fig:test}.

```{r fig-test, echo=FALSE, fig.cap="Test Figure \\label{fig:test}"}
plot(1:10)
